### 2021-04-22 input/introduction.tex
intro until contribution , In this paper [...]

These approaches directly contradict with the objectives of Edge
infrastructures that aim at reducing the impact of latency as well as
the volume of data passing through the network.
%
First, accessing a remote \node to request content location(s) raises
hot spots and availability issues. But most importantly, it results in
additional delays that occur even before the actual download
started~\cite{asrese2019measuring, doan2019tracing}.
%
Second, the client gets a list of content locations at the discretion
of content indexing services. Without information about these
locations, it often ends up downloading from multiple replica hosts,
yet only keeping the fastest answer~\REF. In turns, either a client wastes
network resources, or faces lower response time.
%% there is no information to select the ``best'' node among the possible
%% candidates from which the content could be retrieved. In most cases,
%% this results in parallel requests performed by the client node to each
%% candidate with the goal of retrieving the content as efficient as
%% possible.

A ``simple'' way to tackle the aforementioned limitations would be to
maintain on each node composing the infrastructure and for each
content, an index of all replicas (and their ``distance'').  In such
an approach, each time a new replica is created or deleted, a message
is broadcasted from the node that performed the operation (\ie the
source) to all nodes, increasing the distance information at each hop.
%
In addition to being complicated for large-scale systems, maintaining
a global view on each node is useless as there is no interest to
inform a node of the creation/removal of a replica at the opposite of
the network (each node trying to get content from the ``closest''
one).  In other words, the broadcast should be limited to a partition
of the infrastructure, (\ie the subset of nodes that has to update the
current location for this particular content). Obviously, these
partitions depend and evolve according to concurrent operations made
by nodes (replica creation/removal) as well as dynamic changes in the
infrastructure (network failures, node apparitions/leaves).

>>>>

These approaches directly contradict with the objectives of Edge
infrastructures that aim at reducing the impact of latency as well as
the volume of data passing through the network.
%
First, accessing a remote \node to request content location(s) raises
hot spots and availability issues. But most importantly, it results in
additional delays that occur even before the actual download
started~\cite{asrese2019measuring, doan2019tracing}.
%
Second, the client gets a list of content locations at the discretion
of content indexing services. Without information about these
locations, it often ends up downloading from multiple replica hosts,
yet only keeping the fastest answer~\REF. In turns, either clients
waste network resources, or face lower response time. 
%% there is no information to select the ``best'' node among the
%% possible candidates from which the content could be retrieved. In
%% most cases, this results in parallel requests performed by the
%% client node to each candidate with the goal of retrieving the
%% content as efficient as possible.

To tackle aforementioned limitations, every \process that might
request or replicate content must also host its own content indexing
service in a fully decentralized fashion~\cite{kermarrec2015want}. At
any time, it can immediately locate the closest replica of specific
content.  A naive approach would be that every \process indexes and
ranks \emph{every live} replica along with its \emph{location}
information. When creating or destroying a replica, a \process would
notify all other \processes by efficiently broadcasting its
operation~\cite{birman1999bimodal, hadzilacos1994modular,
  raynal2013distributed}. Unfortunately, this also contradicts with
Edge infrastructure objectives, for such protocol does not confine the
traffic generated to maintain its indexes. A \process may acknowledge
the existence of replicas at the other side of the network while there
already exists a replica right next to it.

Instead, a \process creating a replica should notify all and only
\processes that have no closer replica. This would create
interconnected sets of \processes, or \emph{partitions}, gathered
around a \emph{source} being their respective replica. A \process
deleting its replica should notify all members of its partition so
they can rally their current closest partition. A periodic
advertisement protocol already provides both these operations for
routing purposes~\cite{hemmati2015namebased}. However, its functioning
requires
\begin{inparaenum}[(i)]
\item to generate traffic even when the system is quiescent, and
\item to finely tune physical-time-based intervals that depend on
  network topology parameters such as network diameter.
\end{inparaenum}

%% A ``simple'' way to tackle the aforementioned limitations would be to
%% maintain on each node composing the infrastructure and for each
%% content, an index of all replicas (and their ``distance'').  In such
%% an approach, each time a new replica is created or deleted, a message
%% is broadcasted from the node that performed the operation (\ie the
%% source) to all nodes, increasing the distance information at each hop.
%% %
%% In addition to being complicated for large-scale systems, maintaining
%% a global view on each node is useless as there is no interest to
%% inform a node of the creation/removal of a replica at the opposite of
%% the network (each node trying to get content from the ``closest''
%% one).  In other words, the broadcast should be limited to a partition
%% of the infrastructure, (\ie the subset of nodes that has to update the
%% current location for this particular content). Obviously, these
%% partitions depend and evolve according to concurrent operations made
%% by nodes (replica creation/removal) as well as dynamic changes in the
%% infrastructure (network failures, node apparitions/leaves).
